The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2013-06-18 script/de/chapters/digitalsignatures.tex
CT Script: Many minor changes (formal improvements and corrections).
CT Script: Minor changes including the section about Shared Primes (currently only in English).

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Aktuelle Angriffe gegen Hashfunktionen wie SHA-1}
\label{collision-attacks-against-sha-1}

@@

Das U.S. National Institute of Standards and Technology (NIST)\index{NIST} hat
schon vor Bekanntwerden der neuen Ergebnisse angekündigt, SHA-1 in den
näch"-sten Jahren auslaufen zu lassen. Es ist daher zu empfehlen, für neue
Produkte zur Erstellung von Sig"-naturen SHA-1 nicht mehr zu verwenden. Die
SHA-2 Familie \cite{ds:FIPS180-3} bietet stärkere Verfahren.  Um den neuen
Erkenntnissen in der Kryptoanalyse von Hashfunktionen Rechnung zu tragen, hat
das NIST 2008 einen Wettbewerb gestartet: Als neue Hashfunktion \glqq SHA-3''
wurde im Oktober 2012 Keccak\index{Keccak} verkündet.\footnote{%
\url{http://csrc.nist.gov/groups/ST/hash/sha-3/}}

@@

\begin{ctsquote}
\glqq Manipulation war Sobols Spezialität ... das Hauptziel der Ermittlungen sollte sein, hinter Sobols Masterplan zu kommen.\grqq 
\caption[Daniel Suarez, Daemon]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, \glqq Daemon\grqq, rororo, (c) 2010,
Kapitel 14, \glqq mem-payload\grqq, S. 148, Ross.}

>>>>

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Aktuelle Angriffe gegen Hashfunktionen // SHA-3}
\label{collision-attacks-against-sha-1}

@@

Das U.S. National Institute of Standards and Technology (NIST)\index{NIST} hat
schon vor Bekanntwerden der neuen Ergebnisse angekündigt, SHA-1 in den
näch"-sten Jahren auslaufen zu lassen. Es ist daher zu empfehlen, für neue
Produkte zur Erstellung von Sig"-naturen SHA-1 nicht mehr zu verwenden. Die
SHA-2 Familie \cite{ds:FIPS180-3} bietet stärkere Verfahren.

Um den neuen Erkenntnissen in der Kryptoanalyse von Hashfunktionen Rechnung
zu tragen, hat das NIST 2008 einen Wettbewerb gestartet, um eine neue
Hash-Funktion jenseits der SHA-2-Familie zu entwickeln: Als neue Hashfunktion
\glqq SHA-3'' wurde im Oktober 2012 Keccak\index{Keccak}\index{SHA-3}
verkündet.\footnote{%
\url{http://csrc.nist.gov/groups/ST/hash/sha-3/}\\
    Mit {\bf CT2}\index{CT2}\index{CrypTool 2} können Sie im Startcenter
    über {\bf Vorlagen \textbackslash{} Hash-Funktionen \textbackslash{}
    Keccak-Hash (SHA-3)} die Keccak-Hashfunktion ausführen und visualisieren.\\
    Keccak kann auch als Zufallszahlengenerator und als Stromchiffre benutzt
    werden: Das finden Sie in den Startcenter-Vorlagen über
    {\bf Werkzeuge \textbackslash{} Keccak PRNG}, bzw. 
    {\bf Kryptographie \textbackslash{} Modern \textbackslash{} Symmetrisch
         \textbackslash{} Keccak-Stromchiffre}.
}

@@

\begin{ctsquote}
\glqq Manipulation war Sobols Spezialität ... das Hauptziel der Ermittlungen sollte sein, hinter Sobols Masterplan zu kommen.\grqq 
\caption[Daniel Suarez]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, \glqq Daemon\grqq, rororo, (c) 2010,
Kapitel 14, \glqq mem-payload\grqq, S. 148, Ross.}

### 2013-06-18 script/de/chapters/menus.tex
CT Script: Minor changes including the section about Shared Primes (currently only in English).

   % Eyecatcher_Neue-CrypTool-Version
Dieser Anhang enthält auf der folgenden Seite den kompletten Menübaum der
CrypTool\index{CrypTool}-Version 1.4.31\footnote{%
  Während sich seit 2010 Änderungen an der langjährig stabilen Version
  CrypTool 1 ({\bf CT1})\index{CrypTool 1} vor allem auf Bugfixes beschränkten,
  fließen viele Neuerungen in die beiden Nachfolgeversionen CrypTool 2
  ({\bf CT2})\index{CrypTool 2} und JCrypTool ({\bf JCT})\index{JCrypTool}
  ein:\\
  - Webseite CT2: \url{http://www.cryptool.org/de/ct2-documentation-de} \\
  - Webseite JCT: \url{http://www.cryptool.org/de/jct-machmit-de} \\
  Diese Nachfolgeversionen sind zur Zeit (Nov. 2012) noch Betaversionen;
  sie stehen aber kurz vor ihrem jeweiligen ersten Release und sind schon
  länger stabil genug, um von Endbenutzern genutzt werden zu können.
}.

@@

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/JCT-Welcome-DE}
\hypertarget{Welcome-Screenshot-JCT}{}
\caption{Willkommen-Fenster in JCT (RC6, Juli 2012)} 
\label{Welcome-Screenshot-JCT}
\end{center}
\end{figure}
%\clearpage
Mit Klick auf \glqq Start'' kann man die verschiedenen Funktionen direkt nutzen.
Die in JCT implementierten Funktionen werden über zwei unterschiedliche Perspektiven angeboten:
\begin{itemize}
   \item Standard-Perspektive
   \item Funktional-Perspektive
 \end{itemize}

@@

Alle Funktionen der {\bf Funktional-Perspektive} finden sich in der \glqq Algorithmen'' genannten Navigationsleiste (in dieser Perspektive ebenfalls rechts). Die Funktional-Perspektive enthält alle Detaileinstellungen der verschiedenen Algorithmen und bietet insbesondere auch Algorithmen aus dem Bereich des Post-Quantum-Computings\index{Post-Quantum-Computing} an.

>>>>

   % Eyecatcher_Neue-CrypTool-Version
Dieser Anhang enthält auf der folgenden Seite den kompletten Menübaum der
CrypTool\index{CrypTool}-Version 1.4.31\footnote{%
  Während sich seit 2010 Änderungen an der langjährig stabilen Version
  CrypTool 1 ({\bf CT1})\index{CrypTool 1}\index{CT1} vor allem auf Bugfixes
  beschränkten, fließen viele Neuerungen in die beiden Nachfolgeversionen
  CrypTool 2 ({\bf CT2})\index{CrypTool 2}\index{CT2} und JCrypTool
  ({\bf JCT})\index{JCrypTool}\index{JCT} ein:\\
  - Webseite CT2: \url{http://www.cryptool.org/de/ct2-documentation-de} \\
  - Webseite JCT: \url{http://www.cryptool.org/de/jct-machmit-de} \\
  Diese Nachfolgeversionen sind zur Zeit (Nov. 2012) noch Betaversionen;
  sie stehen aber kurz vor ihrem jeweiligen ersten Release und sind schon
  länger stabil genug, um von Endbenutzern genutzt werden zu können.
}.

@@

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/JCT-Welcome-DE}
\hypertarget{Welcome-Screenshot-JCT}{}
\caption{Willkommen-Fenster in JCT (RC6, Juli 2012)} 
\label{Welcome-Screenshot-JCT}
\end{center}
\end{figure}
%\clearpage
Mit Klick auf \glqq Start'' kann man die verschiedenen Funktionen direkt nutzen.
Die in JCT implementierten Funktionen werden über zwei unterschiedliche Perspektiven angeboten:
\begin{itemize}
   \item Standard-Perspektive
   \item Algorithmen-Perspektive
 \end{itemize}

@@

Alle Funktionen der {\bf Algorithmen-Perspektive} finden sich in der \glqq Algorithmen'' genannten Navigationsleiste (in dieser Perspektive ebenfalls rechts). Die Algorithmen-Perspektive enthält alle Detaileinstellungen der verschiedenen Algorithmen und bietet insbesondere auch Algorithmen aus dem Bereich des Post-Quantum-Computings\index{Post-Quantum-Computing} an.

### 2013-06-18 script/de/chapters/numbertheory.tex
CT Script: Minor changes including the section about Shared Primes (currently only in English).

\noindent Als Zyklus bezeichnet man hier eine Folge von Zahlen $a^i{\rm ~mod~}n$
mit $1\leq i<n$
für ein festes $a$, wobei sich die Folge wiederholt. Innerhalb eines Zyklus kommt
jede Zahl nur einmal vor. Allgemeine Zyklen müssen die $1$ nicht enthalten -- im
Gegensatz zu Zyklen, die eine multiplikative Ordnung $\ge 1$ haben (diese haben
die $1$ sogar immer am Ende des Zyklus).\\
Im Folgenden bezeichnet $l$ die Zykluslänge.

@@

% --------------------------------------------------------------------------
\vskip +20pt
\subsubsection{\glqq Shared Primes\grqq: Module mit gleichen Primzahlen}
\label{nt_Shared-Primes} \index{Primzahl!Shared} 
%~\ref{nt_Shared-Primes}, S.~\pageref{nt_Shared-Primes}
Im xxxxxxxxxx

>>>>

\noindent Als Zyklus bezeichnet man hier eine Folge von Zahlen $a^i{\rm ~mod~}n$
mit $1\leq i<n$ für ein festes $a$, wobei sich die Folge wiederholt. Hier kommt
innerhalb eines Zyklus jede Zahl nur einmal vor (aufgrund der Erzeugung als
modulare Potenz). Die Zyklen hier müssen die $1$ nicht enthalten -- es sei
denn, dieser Zyklus gehört zu einer multiplikativen Ordnung $\ge 1$
(diese haben die $1$ immer am Ende des Zyklus und an der Stelle
$a^{n-1} ~mod~n$).\\
\noindent Im Folgenden bezeichnet $l$ die Zykluslänge.

@@

% --------------------------------------------------------------------------
\vskip +20pt
\subsubsection{\glqq Shared Primes\grqq: Module mit gleichen Primzahlen}
\label{nt_Shared-Primes} \index{Primzahl!Shared} 
%~\ref{nt_Shared-Primes}, S.~\pageref{nt_Shared-Primes}

yyyyyyyyyyyyyyyyyyyyyyyyy

### 2013-06-18 script/de/script-de.tex
CT script: Minor formal changes in chapter 4
Several minor changes (for consistency and correctness), mostly in chap 4.
Added chap 8 (HE) from Dr. Martin Franz. Plus some minor changes.
center citations
CT Script: Added 48th M-Prime and some minor changes (DE and EN)
CT-Script: Minor change (SAT solver added in chap 1).
CT Script: Minor changes including the section about Shared Primes (currently only in English).

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}   % SR_2009: added new cover

@@

\floatstyle{boxed}
\newfloat{ctsquote}{H}{loq}   % ctsQuotes-from-Books
\floatname{ctsquote}{Zitat}

@@

\input{chapters/cryptomethods.tex}
\input{chapters/paper_and_pencil.tex}
\input{chapters/primes.tex}
\input{chapters/numbertheory.tex}
\input{chapters/moderncryptography.tex}
\input{chapters/digitalsignatures.tex}
\input{chapters/ellipticcurves.tex}
\bibliographyunit[\chapter]
\bibliography*{references}
\bibliographystyle*{plain}
\input{chapters/crypto2020.tex}
\bibliographyunit

@@

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Verzeichnis der Zitate}
\listof{ctsquote}{Verzeichnis der Zitate}
\index{Zitate}
\label{sc:List-of-Quotes}

@@

\vspace{30pt}
\begin{itemize}
  \item Der Quellcode der Sage-Beispiele in diesem Skript wird in Form von
        Sage-Programmdatei"-en mit dem CrypTool 1-Setup-Programm ausgeliefert.
        Die Beispiele in einem Kapitel sind jeweils in einer Datei zusammen gefasst.\\
        Nach der Installation von CrypTool 1 \index{CrypTool 1} finden Sie
        die Sage-Beispiele im Unterverzeichnis \verb#sage# innerhalb des
        CrypTool 1-Verzeichnisses:\\
        - SAGE-Samples-in-Chap01.sage \\
        - SAGE-Samples-in-Chap02.sage \\
        - SAGE-Samples-in-Chap03.sage \\
        - SAGE-Samples-in-Chap04.sage
  \item Alle Beispiel wurden mit der Sage-Version 5.3 (Release Date 2012-09-08) getestet.
\end{itemize}   % xxxxxxxxxxxxxx Weitere Beispiele ergänzen !

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{fancyvrb}
\usepackage{makeidx}
\usepackage[pdftex]{graphicx}
\usepackage{pdfpages}   % SR_2009: added new cover
\usepackage{paralist} %BE_2012: eliminate space after end{itemize} worked
                      %         with compactitem
\usepackage{arydshln} %BE_Jan2013: To use hdashline
\usepackage{verse}    %BE_Feb2013: To use \settowidth{\versewidth}{xxx}

@@

\floatstyle{boxed}
\newfloat{ctsquotefloat}{H}{loq}   % ctsQuotes-from-Books
\floatname{ctsquotefloat}{Zitat}
\newenvironment{ctsquote}{\begin{ctsquotefloat}\center}{\end{ctsquotefloat}}

@@

\input{chapters/cryptomethods.tex}
\input{chapters/paper_and_pencil.tex}
\input{chapters/primes.tex}
\input{chapters/numbertheory.tex}
\input{chapters/moderncryptography.tex}
\input{chapters/digitalsignatures.tex}
\input{chapters/ellipticcurves.tex}
\input{chapters/homomorphicencryption.tex}
\bibliographyunit[\chapter]
\bibliography*{references}
\bibliographystyle*{plain}
\input{chapters/crypto2020.tex}
\bibliographyunit

@@

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Verzeichnis der Zitate}
\listof{ctsquotefloat}{Verzeichnis der Zitate}
\index{Zitate}
\label{sc:List-of-Quotes}

@@

\vspace{30pt}
\begin{itemize}
  \item Der Quellcode der Sage-Beispiele in diesem Skript wird in Form von
        Sage-Programmdatei"-en mit dem CrypTool 1-Setup-Programm ausgeliefert.
        Die Beispiele in einem Kapitel sind jeweils in einer Datei zusammen gefasst.\\
        Nach der Installation von CrypTool 1 \index{CrypTool 1} finden Sie
        die Sage-Beispiele im Unterverzeichnis \verb#sage# in den folgenden
        4 Dateien:\\
        - SAGE-Samples-in-Chap01.sage \\
        - SAGE-Samples-in-Chap02.sage \\
        - SAGE-Samples-in-Chap03.sage \\
        - SAGE-Samples-in-Chap04.sage
  \item Alle Beispiel wurden mit der Sage-Version 5.3 (Release Date 2012-09-08) getestet.
\end{itemize}   % xxxxxxxxxxxxxx Weitere Beispiele ergänzen !

@@

\newpage %Nice-to-have-TODO_Doesn't seem to create an empty page at the end.
\newpage

### 2013-06-18 script/en/chapters/cryptomethods.tex
CT Script: Many minor changes (formal improvements and corrections).
CT Script: Minor changes including the section about Shared Primes (currently only in English).

\begin{ctsquote}
``Transparency. That's the best one can hope for in a technologically advanced society ... otherwise you will just be manipulated.''
\caption[Daniel Suarez, Freedom]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, ``Freedom'',
   Dutton Adult, 2010, Chapter 5, ``Getting with the Program'', p. 63, Price.}

@@

The mathematicians Courtois and Pieprzyk \cite{cm:Courtois2002} published a paper
in 2002, which got a great deal of attention amongst the cryptology community: The
pair had further developed the XL-method (eXtended Linearization), introduced at
Eurocrypt 2000 by Shamir et al., to create the so called XSL-method (eXtended
Sparse Linearization). The XL-method is a heuristic technique, which in some
cases manages to solve big non-linear equation systems and which was till then
used to analyze an asymmetric algorithm (HFE).  The innovation of Courtois and
Pieprzyk was, to apply the XL-method on symmetric codes: the XSL-method can be
applied to very specific equation systems. A 256-bit AES could be attacked in
roughly $2^{230}$ steps. This is still a purely academic attack, but also a
direction pointer for a complete class of block ciphers. The major problem with
this attack is that until now nobody has worked out, under what conditions it is
successful: the authors specify in their paper necessary conditions, but it is
not known, which conditions are sufficient.  There are two very new aspects of
this attack: firstly this attack is not based on statistics but on algebra. So
attacks seem to be possible, where only very small amounts of ciphertext are
available. Secondly the security of a product algorithm%
\index{Product algorithm}\index{Encryption!Product algorithm}%
\index{Cascade cipher}\index{Encryption!Cascade cipher}%
\footnote{%
A ciphertext can be used as input for another encryption algorithm. 
A cascade cipher%
\index{Product algorithm}\index{Encryption!Product algorithm}%
\index{Cascade cipher}\index{Encryption!Cascade cipher}%
is build up as a composition of different encryption transformations.
The overall cipher is called product algorithm or cascade cipher
(sometimes depending whether the used keys are statistically dependent or not).\\
Cascading does not always improve the security.\\
This process is also used {\em within} modern algorithms:
They usually combine simple and, considered at its own, cryptologically
relatively insecure single steps in several rounds into an efficient 
overall procedure.  Most block ciphers (e.g. DES, IDEA) are cascade ciphers.\\
Also serial usage of the same cipher with different keys (like with Triple-DES)
is called cascade cipher. 
}
does not exponentially increase with the number of rounds.

>>>>

\begin{ctsquote}
``Transparency. That's the best one can hope for in a technologically advanced society ... otherwise you will just be manipulated.''
\caption[Daniel Suarez]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, ``Freedom'',
   Dutton Adult, 2010, Chapter 5, ``Getting with the Program'', p. 63, Price.}

@@

The mathematicians Courtois and Pieprzyk \cite{cm:Courtois2002} published a paper
in 2002, which got a great deal of attention amongst the cryptology community: The
pair had further developed the XL-method (eXtended Linearization), introduced at
Eurocrypt 2000 by Shamir et al., to create the so called XSL-method (eXtended
Sparse Linearization). The XL-method is a heuristic technique, which in some
cases manages to solve big non-linear equation systems and which was till then
used to analyze an asymmetric algorithm (HFE).  The innovation of Courtois and
Pieprzyk was, to apply the XL-method on symmetric codes: the XSL-method can be
applied to very specific equation systems. A 256-bit AES could be attacked in
roughly $2^{230}$ steps. This is still a purely academic attack, but also a
direction pointer for a complete class of block ciphers. The major problem with
this attack is that until now nobody has worked out, under what conditions it is
successful: the authors specify in their paper necessary conditions, but it is
not known, which conditions are sufficient.  There are two very new aspects of
this attack: firstly this attack is not based on statistics but on algebra. So
attacks seem to be possible, where only very small amounts of ciphertext are
available. Secondly the security of a product algorithm%
\index{Product algorithm}\index{Encryption!product algorithm}%
\index{Cascade cipher}\index{Encryption!cascade cipher}%
\footnote{%
A ciphertext can be used as input for another encryption algorithm. 
A cascade cipher%
\index{Product algorithm}\index{Encryption!product algorithm}%
\index{Cascade cipher}\index{Encryption!cascade cipher}%
is build up as a composition of different encryption transformations.
The overall cipher is called product algorithm or cascade cipher
(sometimes depending whether the used keys are statistically dependent or not).\\
Cascading does not always improve the security.\\
This process is also used {\em within} modern algorithms:
They usually combine simple and, considered at its own, cryptologically
relatively insecure single steps in several rounds into an efficient 
overall procedure.  Most block ciphers (e.g. DES, IDEA) are cascade ciphers.\\
Also serial usage of the same cipher with different keys (like with Triple-DES)
is called cascade cipher. 
}
does not exponentially increase with the number of rounds.

### 2013-06-18 script/en/chapters/digitalsignatures.tex
CT Script: Many minor changes (formal improvements and corrections).
CT Script: Minor changes including the section about Shared Primes (currently only in English).

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Current attacks against hash functions like SHA-1}
\label{collision-attacks-against-sha-1}

@@

Already before Crypto 2004 the U.S. National Institute of Standards and
Technology (NIST)\index{NIST} announced, to discontinue SHA-1 in the next few
years. So it is recommended not to use SHA-1 for new products generating digital
signatures. The SHA-2 family \cite{ds:FIPS180-3} provides stronger algorithms.
To address new findings in cryptanalysis, NIST has opened a competition to develop a new cryptographic hash algorithm in 2008: In October 2012
Keccak\index{Keccak} was announced as ``SHA-3''.\footnote{%
\url{http://csrc.nist.gov/groups/ST/hash/sha-3/}}

@@

\begin{ctsquote}
``Manipulation was Sobol's speciality ... the main investigation should brach off and try to discover Sobol's master plan.''
\caption[Daniel Suarez, Daemon]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, ``Daemon'', Dutton Adult, 2010,
Chapter 14, ``Meme Payload'', p. 142, Ross.}

>>>>

% --------------------------------------------------------------------------
\vskip + 15pt
\subsection{Current attacks against hash functions  //  SHA-3}
\label{collision-attacks-against-sha-1}

@@

Already before Crypto 2004 the U.S. National Institute of Standards and
Technology (NIST)\index{NIST} announced, to discontinue SHA-1 in the next few
years. So it is recommended not to use SHA-1 for new products generating digital
signatures. The SHA-2\index{SHA-2} family \cite{ds:FIPS180-3} provides stronger algorithms.

To address new findings in cryptanalysis, in 2008 NIST opened a competition to
develop a new cryptographic hash algorithm beyound the SHA-2 family: In October
2012 Keccak\index{Keccak}\index{SHA-3} was announced as ``SHA-3''.\footnote{%
\url{http://csrc.nist.gov/groups/ST/hash/sha-3/}\\
    With {\bf CT2}\index{CT2}\index{CrypTool 2} you can execute and visualize
    the Keccak hash function -- using in the Startcenter
    {\bf Templates \textbackslash{} Hash Functions \textbackslash{}
    Keccak Hash (SHA-3)}.\\
    Keccak also can be used as pseudo random number generator and as stream
    cipher: This can be found within the Startcenter templates via
    {\bf Tools \textbackslash{} Keccak PRNG}, and 
    {\bf Cryptography \textbackslash{} Modern Ciphers \textbackslash{}
         Symmetric \textbackslash{} Keccak Streamcipher}.
}

@@

\begin{ctsquote}
``Manipulation was Sobol's speciality ... the main investigation should brach off and try to discover Sobol's master plan.''
\caption[Daniel Suarez]{Daniel Suarez\footnotemark}\index{Suarez, Daniel}
\end{ctsquote}
\addtocounter{footnote}{0}\footnotetext{Daniel Suarez, ``Daemon'', Dutton Adult, 2010,
Chapter 14, ``Meme Payload'', p. 142, Ross.}

### 2013-06-18 script/en/chapters/menus.tex
Some minor changes because of warnings with TeXworks.
CT Script: Minor changes including the section about Shared Primes (currently only in English).

This appendix contains at the following page the complete menu tree of
CrypTool\index{CrypTool} version 1.4.31\footnote{%
  Since 2010, changes for the stable CrypTool 1 ({\bf CT1})\index{CrypTool 1}
  focus mainly on bugfixes. Many new developments go into the two successor
  versions CrypTool 2 ({\bf CT2})\index{CrypTool 2} and
  JCrypTool ({\bf JCT})\index{JCrypTool}:\\
  - Web site CT2: \url{http://www.cryptool.org/en/ct2-documentation-en} \\
  - Web site JCT: \url{http://www.cryptool.org/en/jct-volunteer-en} \\
  These successor versions are currently (Nov. 2012) still beta versions;
  but they are close to their first release and they are stable enough
  since quite a while to be used by end-users.\\
}.

@@

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/JCT-Welcome-EN}
\hypertarget{Welcome-Screenshot-JCT}{}
\caption{Welcome screenshot in JCT (RC6, July 2012)} 
\label{Welcome-Screenshot-JCT}
\end{center}
\end{figure}
%\clearpage
After pressing ``Start'' you can directly use the different functions.
The functions implemented in JCT are presented in two different perspectives:
\begin{itemize}
   \item Default Perspective
   \item Funktional Perspective
 \end{itemize}

@@

All functions of the {\bf Functional Perspective} can be found in the navigation bar called ``Algorithms'' (in this perspective also at the right side).
The Functional Perspective contains all detail settings of the various algorithms, it especially offers post-quantum computing algorithmss\index{Post-quantum computing}.

@@

\noindent The following screenshot shows the crypto functions implemented on CTO:
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-1}
\hypertarget{functions-overview-1-CTO}{}
\caption{Screenshot of the functions of CTO (November 2012)} 
\label{functions-overview-1-JCT}
\end{center}
\end{figure}
\clearpage

>>>>

This appendix contains at the following page the complete menu tree of
CrypTool\index{CrypTool} version 1.4.31\footnote{%
  Since 2010, changes for the stable CrypTool 1 ({\bf CT1})\index{CrypTool 1}
  \index{CT1} focus mainly on bugfixes. Many new developments go into the two
  successor versions CrypTool 2 ({\bf CT2})\index{CrypTool 2}\index{CT2} and
  JCrypTool ({\bf JCT})\index{JCrypTool}\index{JCT}:\\
  - Web site CT2: \url{http://www.cryptool.org/en/ct2-documentation-en} \\
  - Web site JCT: \url{http://www.cryptool.org/en/jct-volunteer-en} \\
  These successor versions are currently (Nov. 2012) still beta versions;
  but they are close to their first release and they are stable enough
  since quite a while to be used by end-users.\\
}.

@@

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/JCT-Welcome-EN}
\hypertarget{Welcome-Screenshot-JCT}{}
\caption{Welcome screenshot in JCT (RC6, July 2012)} 
\label{Welcome-Screenshot-JCT}
\end{center}
\end{figure}
%\clearpage
After pressing ``Start'' you can directly use the different functions.
The functions implemented in JCT are presented in two different perspectives:
\begin{itemize}
   \item Default Perspective
   \item Algorithm Perspective
 \end{itemize}

@@

All functions of the {\bf Algorithm Perspective} can be found in the navigation bar called ``Algorithms'' (in this perspective also at the right side).
The Algorithm Perspective contains all detail settings of the various algorithms, it especially offers post-quantum computing algorithms\index{Post-quantum computing}.

@@

\noindent The following screenshot shows the crypto functions implemented on CTO:
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-1}
\hypertarget{functions-overview-1-CTO}{}
\caption{Screenshot of the functions of CTO (November 2012)} 
\label{functions-overview-1-CTO}
\end{center}
\end{figure}
\clearpage
